Towards Practical First-Order Model Counting

### 2024-08-15 doc/paper/paper.tex
A version good enough to submit?

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\newcommand{\expr}{\mathtt{expr}}
\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
\newcommand{\FO}{$\mathsf{FO}$}
\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{CC}$}
\newcommand{\Cranetwo}{\textsc{Crane2}}
\newcommand{\Cranebfs}{\textsc{Crane2-BFS}}
\newcommand{\Cranegreedy}{\textsc{Crane2-Greedy}}

@@

\begin{abstract}
	First-order model counting (FOMC) is the problem of counting the number of models of a sentence in first-order logic. Since lifted inference techniques rely on reductions to variants of FOMC, the design of scalable methods for FOMC has attracted attention from both theoreticians and practitioners over the past decade. Recently, a new approach based on first-order knowledge compilation was proposed. This approach, called \textsc{crane}, instead of simply providing the final count, generates definitions of (possibly recursive) functions that can be evaluated with different arguments to compute the model count for any domain size. However, this approach is not fully automated, as it requires manual evaluation of the constructed functions. The primary contribution of this work is a fully automated compilation algorithm, called \textsc{crane2}, which transforms the function definitions into C++ code equipped with arbitrary-precision arithmetic. These additions allow the new FOMC algorithm to scale to domain sizes over \num{500000} times larger than the current state of the art, as demonstrated through experimental results.

%While \textsc{crane} was shown to handle formulas beyond the capabilites of prior state of the art approaches, the \textsc{crane} still required manual evaluation of constructed functions to obtain model counts. The primary contribution of our work is a fully automated FOMC algorithm that relies on function construction. 
%  
%  the algorithm did not include base cases in the recursive definitions. This
%  work makes three contributions. First, we demonstrate how to construct
%  function definitions that include base cases by modifying the logical formulas
%  used in the FOMC algorithm. Second, we extend the well-known circuit
%  modification technique in knowledge compilation, known as smoothing, to work
%  with the formulas corresponding to base cases. Third, we introduce a
%  compilation algorithm that transforms the function definitions into C++ code,
%  equipped with arbitrary-precision arithmetic. These additions allow the new
%  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
%  the current state of the art, as demonstrated through experimental results.
\end{abstract}

@@

% 1. What is the problem?

\emph{First-order model counting} (FOMC) is the task of counting the number of
models of a sentence in first-order logic over some given domain(s). The
weighted variant of this problem, known as WFOMC, seeks to compute the total
weight of the models~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is related to
its propositional predecessor weighted model
counting~\cite{DBLP:journals/ai/ChaviraD08} and other attempts to unify logic
and
probability~\cite{DBLP:journals/ai/Nilsson86,novak2012mathematical,vsaletic2024graded}.
It is also a key approach to \emph{lifted inference}, which aims to compute
probabilities more efficiently by leveraging symmetries in the
problem~\cite{DBLP:conf/ecai/Kersting12}.

% 2. Why is it interesting and important?

Lifted inference is an active area of research, with recent work in domains such
as constraint satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23} and
probabilistic answer set programming~\cite{DBLP:journals/ijar/AzzoliniR23}.
WFOMC has been used for inference on probabilistic
databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. FOMC algorithms have been
utilised for discovering new integer
sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23}, and for
conjecturing~\cite{DBLP:conf/ilp/BarvinekB0ZK21} and
constructing~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other
recursive structures that describe these sequences. FOMC algorithms have also
been extended to perform
\emph{sampling}~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}.

% By considering domains of increasing sizes, the FOMC of a formula can be seen
% as an integer sequence.

@@

The complexity of FOMC is typically characterised in terms of \emph{data
  complexity}. If there is an algorithm that can compute the FOMC of a formula
in polynomial time with respect to the domain size(s), that formula is called
\emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}.
\citeauthor{DBLP:conf/pods/BeameBGS15}~\shortcite{DBLP:conf/pods/BeameBGS15}
demonstrated the existence of an unliftable formula with three variables. It is
also known that formulas with up to two variables are
liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}. The liftable
fragment of formulas with two variables has been expanded with various
axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23}, counting
quantifiers~\cite{DBLP:journals/jair/Kuzelka21} and in other
ways~\cite{DBLP:conf/nips/KazemiKBP16}.

% This involves fixing the formula and determining whether an
% algorithm exists that can compute the FOMC in time polynomial with respect to
% the domain size(s).

@@

There are many FOMC algorithms with different underlying principles. Perhaps the
most prominent class of FOMC algorithms is based on \emph{first-order knowledge
  compilation} (FOKC). In this approach, the formula is compiled into a
representation (such as a circuit or graph) by applying \emph{compilation
  rules}. Algorithms in this class include
\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its extension
\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. Another FOMC algorithm,
\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, is based on cell enumeration.
Other algorithms utilise local search~\cite{DBLP:journals/pvldb/NiuRDS11},
junction trees~\cite{DBLP:conf/aaai/VenugopalSG15}, Monte Carlo
sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime approximation via
upper/lower bound construction~\cite{DBLP:conf/ijcai/BremenK20}.

% This representation can then be used to compute the FOMC for any combination
% of domain sizes.

% The former compiles formulas into circuits, while the latter compiles them
% first to graphs and then to (algebraic) equations.

@@

The recently proposed \textsc{Crane} algorithm marked significant progress in
handling formulas beyond the capabilities of \textsc{FastWFOMC} and
\textsc{ForcLift}, yet it fell short in critical aspects. \textsc{Crane} was
incomplete since it could only construct function definitions, requiring users
to manually evaluate these functions to obtain model counts. This limitation
prevented \textsc{Crane} from serving as a convenient black box solution for
FOMC. Furthermore, it introduced recursive functions without defining necessary
base cases, adding further complexity to the users. In this work, we present
\Cranetwo{}, addressing these gaps and pushing scalability to unprecedented
levels. Unlike its predecessor, \Cranetwo{} is a fully automated FOMC algorithm,
capable of handling domain sizes over \num{500000} times larger than previous
algorithms.

\Cref{fig:overview} outlines the workflow of the new algorithm. In
\cref{sec:main}, we describe how \CompileWithBaseCases finds base cases for
recursive functions. \Cref{sec:smoothing} explains post-processing techniques to
preserve the correct model count. \Cref{sec:cpp} elucidates how function
definitions are compiled into C++ programs. Note that a solution to FOMC that
uses compilation to C++ has been considered
before~\cite{DBLP:conf/kr/KazemiP16}, however, the extent of formulas that could
be handled was limited. Finally, \cref{sec:experiments} presents experimental
results comparing \Cranetwo{} with other FOMC algorithms.

% by:
% \begin{enumerate*}[label=(\roman*)]
%   \item identifying a sufficient set of base cases for each function,
%   \item constructing formulas corresponding to these base cases,
%   and\label[step]{step2}
%   \item recursing on these new formulas.
% \end{enumerate*}

\section{Preliminaries}

@@

\section{Completing the Definitions of Functions}\label{sec:main}

@@

\Cref{alg:compilewithbasecases} presents our overall approach for compiling a
formula into equations that include the necessary base cases. To begin, we use
the FOKC algorithm of the original \textsc{Crane} to compile the formula into
the three components: $\mathcal{E}$, $\mathcal{F}$, and $\mathcal{D}$. After
some algebraic simplification, $\mathcal{E}$ is passed to the \FindBaseCases
procedure (see \cref{sec:identifying}). For each base case $f(\mathbf{x})$, we
retrieve the logical formula $\mathcal{F}(f)$ associated with the function name
$f$ and simplify it using the \Propagate procedure (explained in detail in
\cref{sec:simplifying}). We do this by iterating over all indices of
$\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate to simplify
$\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$. Finally, on
\cref{line:final}, \CompileWithBaseCases recurses on these simplified formulas
and adds the resulting base case equations to $\mathcal{E}$.
\Cref{example:overall} below provides more detail.

@@

\subsection{Propagating Domain Size Assumptions}\label{sec:simplifying}

@@

\section{Smoothing the Base Cases}\label{sec:smoothing}

@@

\section{Generating C++ Code}\label{sec:cpp}

@@

For
evaluation purposes, we ran each algorithm on each benchmark using domains of
sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a domain size due to timeout, out of memory error, or out of precision errors. While we separately measured compilation and inference time but primarily
focused on total runtime, dominated by the latter.

@@

\section{Conclusion and Future Work}

In this work, we present a scalable automated first-order knowledge compilation-based approach to first order model counting. The proposed approach relies on automatically generating the C++ code corresponding to the recursive functions extracted from knowledge compilation. The enusing empirical evaluatino demonstrated  that \Cranetwo{} can scale to much larger
domain sizes than \textsc{FastWFOMC} while handling more formulas than
\textsc{ForcLift}. Having FOMC algorithms that can efficiently handle large
domain sizes is especially crucial in the weighted setting. For example,
consider the `friends' instance examined in \cref{sec:experiments}, which models
a social network with friendships, smoking habits, and the probability of having
cancer. The utility of such a model would be significantly limited if
probabilities could only be efficiently computed for networks of at most
\num{1000} people.

There are many potential avenues for future work. Specifically, a more thorough
experimental study is needed to understand how FOMC algorithms compare in terms
of their ability to handle different formulas and their scalability with respect
to domain size. Additionally, further characterisation of the capabilities of
\Cranetwo{} can be explored. For example, \emph{completeness} could be proven
for a fragment of first-order logic such as \Ctwo{} (using a suitable encoding
of counting quantifiers). Moreover, the efficiency of a FOMC algorithm in
handling a particular formula can be assessed using \emph{fine-grained
  complexity}. In the case of \Cranetwo{}, this can be done by analysing the
equations~\cite{DBLP:conf/kr/DilkasB23}. By doing so, efficiency can be reasoned
about in a more implementation-independent manner by making claims about the
maximum degree of the polynomial that characterises any given solution.

@@

>>>>

\sisetup{group-separator = {,}}

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\newcommand{\expr}{\mathtt{expr}}
\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
\newcommand{\FO}{$\mathsf{FO}$}
\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{CC}$}
\newcommand{\Cranetwo}{\textsc{Gantry}}
\newcommand{\Cranebfs}{\textsc{Gantry-BFS}}
\newcommand{\Cranegreedy}{\textsc{Gantry-Greedy}}

@@

\begin{abstract}
  First-order model counting (FOMC) is the problem of counting the number of
  models of a sentence in first-order logic. Since lifted inference techniques
  rely on reductions to variants of FOMC, the design of scalable methods for
  FOMC has attracted attention from both theoreticians and practitioners over
  the past decade. Recently, a new approach based on first-order knowledge
  compilation was proposed. This approach, called \textsc{Crane}, instead of
  simply providing the final count, generates definitions of (possibly
  recursive) functions that can be evaluated with different arguments to compute
  the model count for any domain size. However, this approach is not fully
  automated, as it requires manual evaluation of the constructed functions. The
  primary contribution of this work is a fully automated compilation algorithm,
  called \Cranetwo{}, which transforms the function definitions into C++ code
  equipped with arbitrary-precision arithmetic. These additions allow the new
  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
  the current state of the art, as demonstrated through experimental results.
\end{abstract}

@@

% 1. What is the problem?
% 2. Why is it interesting and important?

\emph{First-order model counting} (FOMC) is the task of determining the number
of models for a sentence in first-order logic over a specified domain. The
weighted variant, WFOMC, computes the total weight of these models, linking
logical reasoning with probabilistic
frameworks~\cite{DBLP:conf/ijcai/BroeckTMDR11}. It builds upon earlier efforts
in weighted model counting for propositional
logic~\cite{DBLP:journals/ai/ChaviraD08} and broader attempts to bridge logic
and
probability~\cite{DBLP:journals/ai/Nilsson86,novak2012mathematical,vsaletic2024graded}.
WFOMC is central to \emph{lifted inference}, which enhances the efficiency of
probabilistic calculations by exploiting
symmetries~\cite{DBLP:conf/ecai/Kersting12}. Lifted inference continues to
advance, with applications extending to constraint satisfaction
problems~\cite{DBLP:journals/jair/TotisDRK23} and probabilistic answer set
programming~\cite{DBLP:journals/ijar/AzzoliniR23}. Moreover, WFOMC has proven
effective at reasoning over probabilistic
databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. FOMC algorithms have also
facilitated breakthroughs in discovering integer
sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} and developing recurrence
relations for these sequences~\cite{DBLP:conf/kr/DilkasB23}. Recently, these
algorithms have been extended to perform sampling
tasks~\cite{DBLP:journals/ai/WangPWK24}.

@@

The complexity of FOMC is generally measured by \emph{data complexity}, with a
formula classified as \emph{liftable} if it can be solved in polynomial time
relative to the domain size~\cite{DBLP:conf/starai/JaegerB12}. While all
formulas with up to two variables are known to be
liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14},
\citeauthor{DBLP:conf/pods/BeameBGS15}~\shortcite{DBLP:conf/pods/BeameBGS15}
demonstrated that liftability does not extend to all formulas, identifying an
unliftable formula with three variables. Recent work has further extended the
liftable fragment with additional
axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and counting
quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, expanding our understanding of
liftability.

@@

FOMC algorithms are diverse, with approaches ranging from \emph{first-order
  knowledge compilation} (FOKC) to local
search~\cite{DBLP:journals/pvldb/NiuRDS11}, Monte Carlo
sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime
approximation~\cite{DBLP:conf/ijcai/BremenK20}. Among these, FOKC-based
algorithms are particularly prominent, transforming formulas into structured
representations such as circuits or graphs. Notable examples include
\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its successor
\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. Another important algorithm,
\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, uses cell enumeration as its
foundation.

@@

The \textsc{Crane} algorithm marked a significant step forward, expanding the
range of formulas handled by FOMC algorithms. However, it had notable
limitations:
\begin{enumerate*}[label=(\roman*)]
  \item it required manual evaluation of function definitions to compute model
  counts, and
  \item it introduced recursive functions without proper base cases, making it
  more complex to use.
\end{enumerate*}
To address these shortcomings, we present \Cranetwo{}, a fully automated FOMC
algorithm that overcomes the constraints of its predecessor. \Cranetwo{} can
handle domain sizes over \num{500000} times larger than previous algorithms and
simplifies the user experience by automatically handling base cases and
compiling function definitions into efficient C++ programs.

In \cref{sec:preliminaries}, we cover some preliminaries, and in
\cref{sec:main}, we detail all our technical contributions. Finally, in
\cref{sec:experiments}, we present our experimental results, demonstrating
\Cranetwo{}'s performance compared to other FOMC algorithms, and, in
\cref{sec:conclusion}, we conclude the paper by discussing promising avenues for
future work.

\section{Preliminaries}\label{sec:preliminaries}

@@

\section{Technical Contributions}\label{sec:main}

\Cref{fig:overview} provides an overview of \Cranetwo{}'s workflow.
\Cref{sec:completing} describes the main algorithm for completing the
definitions of recursive functions with a sufficient set of base cases.
\Cref{sec:identifying,sec:propagating} describe subsidiary algorithms for
constructing a set of base cases and their corresponding logical formulas.
\Cref{sec:smoothing} explains the post-processing techniques for ensuring
accurate model counting. Additionally, \cref{sec:cpp} explains the process of
compiling function definitions into C++ code, greatly expanding upon the range
of formulas that could previously be handled by similar
approaches~\cite{DBLP:conf/kr/KazemiP16}.

\subsection{Completing the Definitions of Functions}\label{sec:completing}

@@

\Cref{alg:compilewithbasecases} presents our overall approach for compiling a
formula into equations that include the necessary base cases. To begin, we use
the FOKC algorithm of the original \textsc{Crane} to compile the formula into
the three components: $\mathcal{E}$, $\mathcal{F}$, and $\mathcal{D}$. After
some algebraic simplification, $\mathcal{E}$ is passed to the \FindBaseCases
procedure (see \cref{sec:identifying}). For each base case $f(\mathbf{x})$, we
retrieve the logical formula $\mathcal{F}(f)$ associated with the function name
$f$ and simplify it using the \Propagate procedure (explained in detail in
\cref{sec:propagating}). We do this by iterating over all indices of
$\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate to simplify
$\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$. Finally, on
\cref{line:final}, \CompileWithBaseCases recurses on these simplified formulas
and adds the resulting base case equations to $\mathcal{E}$.
\Cref{example:overall} below provides more detail.

@@

\subsection{Propagating Domain Size Assumptions}\label{sec:propagating}

@@

\subsection{Smoothing the Base Cases}\label{sec:smoothing}

@@

\subsection{Generating C++ Code}\label{sec:cpp}

@@

For evaluation purposes, we ran each algorithm on each benchmark using domains
of sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a
domain size due to timeout, out of memory error, or out of precision errors.
While we separately measured compilation and inference time, we primarily focus
on total runtime, dominated by the latter.

@@

\section{Conclusion and Future Work}\label{sec:conclusion}

In this work, we have presented a scalable automated FOKC-based approach to
FOMC. Our algorithm involves completing the definitions of recursive functions
and subsequently translating all function definitions into C++ code. Empirical
results demonstrate that \Cranetwo{} can scale to larger domain sizes than
\textsc{FastWFOMC} while supporting a wider range of formulas than
\textsc{ForcLift}. The ability to efficiently handle large domain sizes is
particularly crucial in the weighted setting, as illustrated by the `friends'
example discussed in \cref{sec:experiments}, where the model captures complex
social networks with probabilistic relationships. Without this scalability, the
practical usefulness of these models would be limited.

Future directions for research include conducting a comprehensive experimental
comparison of FOMC algorithms to better understand their comparative performance
across various formulas. The capabilities of \Cranetwo{} could also be
characterised theoretically, e.g.\ by proving completeness for specific logic
fragments like \Ctwo{}. Additionally, the efficiency of FOMC algorithms can be
further analysed using fine-grained complexity, which would provide more
detailed insights into the computational demands of different formulas.

@@

\section{Reproducibility Checklist}

This paper:
\begin{itemize}
  \item Includes a conceptual outline and/or pseudocode description of AI
        methods introduced (\textbf{yes}/partial/no/NA)
  \item Clearly delineates statements that are opinions, hypothesis, and
        speculation from objective facts and results (\textbf{yes}/no)
  \item Provides well marked pedagogical references for less-familiare readers
        to gain background necessary to replicate the paper (\textbf{yes}/no)
\end{itemize}

Does this paper make theoretical contributions? (\textbf{yes}/no) If yes, please
complete the list below.

\begin{itemize}
  \item All assumptions and restrictions are stated clearly and formally.
        (\textbf{yes}/partial/no)
  \item All novel claims are stated formally (e.g., in theorem statements).
        (\textbf{yes}/partial/no)
  \item Proofs of all novel claims are included. (\textbf{yes}/partial/no)
  \item Proof sketches or intuitions are given for complex and/or novel results.
        (\textbf{yes}/partial/no)
  \item Appropriate citations to theoretical tools used are given.
        (\textbf{yes}/partial/no)
  \item All theoretical claims are demonstrated empirically to hold.
        (\textbf{yes}/partial/no/NA)
  \item All experimental code used to eliminate or disprove claims is included.
        (yes/no/\textbf{NA})
\end{itemize}

Does this paper rely on one or more datasets? (\textbf{yes}/no) If yes, please
complete the list below.

\begin{itemize}
  \item A motivation is given for why the experiments are conducted on the
        selected datasets (\textbf{yes}/partial/no/NA)
  \item All novel datasets introduced in this paper are included in a data
        appendix. (\textbf{yes}/partial/no/NA)
  \item All novel datasets introduced in this paper will be made publicly
        available upon publication of the paper with a license that allows free
        usage for research purposes. (\textbf{yes}/partial/no/NA)
  \item All datasets drawn from the existing literature (potentially including
        authors’ own previously published work) are accompanied by appropriate
        citations. (\textbf{yes}/no/NA)
  \item All datasets drawn from the existing literature (potentially including
        authors’ own previously published work) are publicly available.
        (\textbf{yes}/partial/no/NA)
  \item All datasets that are not publicly available are described in detail,
        with explanation why publicly available alternatives are not
        scientifically satisficing. (\textbf{yes}/partial/no/NA)
\end{itemize}

Does this paper include computational experiments? (\textbf{yes}/no) If yes,
please complete the list below.

\begin{itemize}
  \item Any code required for pre-processing data is included in the appendix.
        (\textbf{yes}/partial/no).
  \item All source code required for conducting and analyzing the experiments is
        included in a code appendix. (\textbf{yes}/partial/no)
  \item All source code required for conducting and analyzing the experiments
        will be made publicly available upon publication of the paper with a
        license that allows free usage for research purposes.
        (\textbf{yes}/partial/no)
  \item All source code implementing new methods have comments detailing the
        implementation, with references to the paper where each step comes from
        (yes/\textbf{partial}/no)
  \item If an algorithm depends on randomness, then the method used for setting
        seeds is described in a way sufficient to allow replication of results.
        (yes/partial/no/\textbf{NA})
  \item This paper specifies the computing infrastructure used for running
        experiments (hardware and software), including GPU/CPU models; amount of
        memory; operating system; names and versions of relevant software
        libraries and frameworks. (\textbf{yes}/partial/no)
  \item This paper formally describes evaluation metrics used and explains the
        motivation for choosing these metrics. (\textbf{yes}/partial/no)
  \item This paper states the number of algorithm runs used to compute each
        reported result. (\textbf{yes}/no)
  \item Analysis of experiments goes beyond single-dimensional summaries of
        performance (e.g., average; median) to include measures of variation,
        confidence, or other distributional information. (\textbf{yes}/no)
  \item The significance of any improvement or decrease in performance is judged
        using appropriate statistical tests (e.g., Wilcoxon signed-rank).
        (\textbf{yes}/partial/no)
  \item This paper lists all final (hyper-)parameters used for each
        model/algorithm in the paper’s experiments. (yes/partial/no/\textbf{NA})
  \item This paper states the number and range of values tried per (hyper-)
        parameter during development of the paper, along with the criterion used
        for selecting the final parameter setting. (yes/partial/no/\textbf{NA})
\end{itemize}
